### 2023-02-23 ART_Dodig-Crnkovic/Dodig-Crnkovic.tex
Editorial corrections added

}
Cognition can be defined as a~process of ``being in the world'' of an agent. For living organisms, cognition is a~process of life (perception, internal process control by information, actuation/agency),
%\label{ref:RNDoh9e7EeRCW}(Maturana, 1970; Maturana and Varela, 1980; Stewart, 1996).
\parencites{maturana_biology_1970}{maturana_autopoiesis_1980}{stewart_cognition_1996}.
Cognition of an organism is based on the ability to learn from the environment and adapt so as to survive as an individual and as a~species, for which organisms use information and its processing (computation).

@@

Biogenic approaches on the other hand broaden the domain, seeing cognition as an ability of all living organisms
%\label{ref:RNDiBBkzuUqVI}(Maturana, 1970; Maturana and Varela, 1980; Stewart, 1996).
\parencites{maturana_biology_1970}{maturana_autopoiesis_1980}{stewart_cognition_1996}

@@

\myquote{
a~component system is a~computer which, when executing its operations (software) builds a~new hardware. [... W]e have a~computer that re-wires itself in a~hardware-software interplay: the hardware defines the software, and the software defines new hardware. Then the circle starts again
%\label{ref:RNDWO7dKBBpPU}(Kampis, 1991, p.223).
\parencite[][p.223]{kampis_self-modifying_1991}.%
}

@@

The essential property of morphological computation is that it is defined on a~structure of nodes (agents) that exchange (communicate) information. It is thus applied not only in robotics, but generalized to other physical information-processing systems, including living beings
%\label{ref:RNDUmZTsrN545}(Dodig-Crnkovic, 2013b; 2017b; 2018).
\parencites[][]{dodig-crnkovic_development_2013}[][]{dodig-crnkovic_morphologically_2017}[][]{dodig-crnkovic_cognition_2018}.%

@@

Starting from the above ideas,
%\label{ref:RNDXDRXw0g64D}(Dodig-Crnkovic, 2007)
\parencite[][]{dodig-crnkovic_epistemology_2007} %
 proposes that epistemology can be naturalized through the info-computational approach to knowledge generation. The computing nature framework (naturalist computationalism) makes it possible to describe all cognizing agents (living organisms and artificial cognitive systems) as informational structures with computational dynamics 
%\label{ref:RNDKrdNppjXiv}(Dodig-Crnkovic and Burgin, 2011; Dodig-Crnkovic, 2013a; 2014b; 2017a; Dodig-Crnkovic and Giovagnoli, 2013; 2017).
\parencites[][]{dodig-crnkovic_dialogue_2011}[][]{dodig-crnkovic_computing_2013}[][]{dodig-crnkovic_modeling_2014}[][]{dodig-crnkovic_computational_2017}[][]{dodig-crnkovic_computing_2013}[][]{dodig-crnkovic_computational_2017}. %
 Morphological computation in this framework is a~process of creation of new informational structures, as it appears in nature, living as non-living. It is a~process of morphogenesis, which in biological systems is driven by development and evolution 
%\label{ref:RNDBhnHdYgrNx}(Dodig-Crnkovic, 2013b; 2017b; 2018).
\parencites[][]{dodig-crnkovic_development_2013}[][]{dodig-crnkovic_morphologically_2017}[][]{dodig-crnkovic_cognition_2018}.%

>>>>

}
Cognition can be defined as a~process of ``being in the world'' of an agent. For living organisms, cognition is a~process of life (perception, internal process control by information, actuation/agency)
%\label{ref:RNDoh9e7EeRCW}(Maturana, 1970; Maturana and Varela, 1980; Stewart, 1996).
\parencites{maturana_biology_1970}{maturana_autopoiesis_1980}{stewart_cognition_1996}.
Cognition of an organism is based on the ability to learn from the environment and adapt so as to survive as an individual and as a~species, for which organisms use information and its processing (computation).

@@

Biogenic approaches on the other hand broaden the domain, seeing cognition as an ability of all living organisms
%\label{ref:RNDiBBkzuUqVI}(Maturana, 1970; Maturana and Varela, 1980; Stewart, 1996).
\parencites{maturana_biology_1970}{maturana_autopoiesis_1980}{stewart_cognition_1996}.

@@

\myquote{
a~component system is a~computer which, when executing its operations (software) builds a~new hardware. [... We] have a~computer that re-wires itself in a~hardware-software interplay: the hardware defines the software, and the software defines new hardware. Then the circle starts again
%\label{ref:RNDWO7dKBBpPU}(Kampis, 1991, p.223).
\parencite[][p.223]{kampis_self-modifying_1991}.%
}

@@

The essential property of morphological computation is that it is defined on a~structure of nodes (agents) that exchange (communicate) information. It is thus applied not only in robotics, but generalized to other physical information-processing systems, including living beings
%\label{ref:RNDUmZTsrN545}(Dodig-Crnkovic, 2013b; 2017b; 2018).
\parencites[][]{muller_info-computational_2013}[][]{dodig-crnkovic_morphologically_2017}[][]{dodig-crnkovic_cognition_2018}.%

@@

Starting from the above ideas,
%\label{ref:RNDXDRXw0g64D}(Dodig-Crnkovic, 2007)
\parencite[][]{dodig-crnkovic_epistemology_2007} %
 proposes that epistemology can be naturalized through the info-computational approach to knowledge generation. The computing nature framework (naturalist computationalism) makes it possible to describe all cognizing agents (living organisms and artificial cognitive systems) as informational structures with computational dynamics 
%\label{ref:RNDKrdNppjXiv}(Dodig-Crnkovic and Burgin, 2011; Dodig-Crnkovic, 2013a; 2014b; 2017a; Dodig-Crnkovic and Giovagnoli, 2013; 2017).
%\parencites[][]{dodig-crnkovic_dialogue_2011}[][]{dodig-crnkovic_computing_2013}[][]{dodig-crnkovic_modeling_2014}[][]{dodig-crnkovic_computational_2017}[][]{dodig-crnkovic_computing_2013}[][]{dodig-crnkovic_computational_2017}. %
\parencites[][]{dodig-crnkovic_information_2011}[][]{dodig-crnkovic_development_2013}[][]{dodig-crnkovic_why_2014}[][]{dodig-crnkovic_computational_2017}[][]{dodig-crnkovic_computing_2013}[][]{dodig-crnkovic_representation_2017}. %
 Morphological computation in this framework is a~process of creation of new informational structures, as it appears in nature, living as non-living. It is a~process of morphogenesis, which in biological systems is driven by development and evolution 
%\label{ref:RNDBhnHdYgrNx}(Dodig-Crnkovic, 2013b; 2017b; 2018).
\parencites[][]{muller_info-computational_2013}[][]{dodig-crnkovic_morphologically_2017}[][]{dodig-crnkovic_cognition_2018}.%
